---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# youngSwimmers

<!-- badges: start -->
[![R-CMD-check](https://github.com/NIM-ACh/youngSwimmers/workflows/R-CMD-check/badge.svg)](https://github.com/NIM-ACh/youngSwimmers/actions)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![CRAN status](https://www.r-pkg.org/badges/version/youngSwimmers)](https://CRAN.R-project.org/package=youngSwimmers)
<!-- badges: end -->

Access data from the young elite swimmers study.

## Installation

You can install the development version of youngSwimmers from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("NIM-ACh/youngSwimmers")
```

## Example

This is a basic example which shows you how to access summary statistics:

```{r example}
library(youngSwimmers) # Load the package

summary(youngswimmers[, 4:6])
```

For more information on the use of the package, please check the article ["Using the youngswimmers dataset"](https://nim-ach.github.io/youngSwimmers/articles/articles/using_data.html). There you will find information for computing descriptive statistics and plotting functionalities.

## Citation

To cite this package, run the next line of code:

```r
citation("youngSwimmers")
```

And you will get the next output:

```{r, echo=FALSE, comment=""}
citation("youngSwimmers")
```

