---
title: "Using the youngswimmers dataset"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(youngSwimmers)
```

# Summary statistics

For summary statistics like mean and standard deviation you can use the base function `mean()` and `sd()`, for median and interquartile range you may use `median()` and `IQR()`. 

But because the data is in [long format](https://en.wikipedia.org/wiki/Wide_and_narrow_data) you must consider its structure in order to analyse it properly.

Lets explore the mean weight for each time period. For that we can use `data.table` for ease (for details on data.table please see [this](https://rdatatable.gitlab.io/data.table/)).

```{r}
library(data.table)

youngswimmers[, .(mean_weight = mean(weight, na.rm = TRUE)), period]
```

But what if we want the mean weight between males and females for each time period? We could write it this way. For that we will use `tapply()` (for nested operations).

```{r}
youngswimmers[, tapply(weight, sex, mean, na.rm = TRUE, simplify = FALSE), period]
```

But we can pass any function that we want into `tapply()` (that returns an object of length one). Lets try create a custom function thah computes the mean and standard deviation.

```{r}
my_mean_and_sd <- function(x) {
  x <- x[!is.na(x)] #remove missing values
  
  mu <- mean(x) # get the mean of x
  sigma <- sd(x) # and standard deviation from x
  
  # We round values into 1 decimal place
  mu <- round(mu, digits = 1)
  sigma <- round(sigma, digits = 1)
  
  result <- paste(mu, "±", sigma) # finally we merge both results into one string
  
  return(result) # and get back the results
}
```

Now lets try our custom function to get the mean and standard deviation of weight between males and females for each time period.

```{r}
youngswimmers[, tapply(weight, sex, my_mean_and_sd, simplify = FALSE), period]
```

You can replace weigth for any of the variables available in the dataset. For details on the dataset, check the documentation on `youngSwimmers::youngswimmers`.

# Plot the data

For plotting you can use your favourite library (ggplot2, lattice, base-r, etc). Lets try an example with base-r plotting system.

For this example lets plot the change of mean weight across time periods between males and females.

```{r}
# Get variables (first bracket) and then drop missing values (second bracket)
plot_data <- youngswimmers[, .(sex, period, weight)][, na.omit(.SD)] 

# Plot data using the mean
plot_data[, interaction.plot(period, sex, weight, fun = mean)]

# Now plot data using the median
plot_data[, interaction.plot(period, sex, weight, fun = median)]
```

Quite an interesting picture! Now lets try a boxplot of weight across time grouped by sex (sounds hard to do, but not really). Here we will use `ggplot2` package, for details see [this](https://ggplot2.tidyverse.org).

```{r}
# First load ggplot2
library(ggplot2)

ggplot(youngswimmers, aes(x = period, y = weight, fill = sex)) +
  geom_boxplot()
```

In just two lines of code we reproduce an awesome and informative graph. `ggplot2` is a powerful library based on *The Grammar of Graphics*.
